The College Application Problem

### 2022-06-13 slides_25min/slides.tex
add reference to Nemhauser and Wolsey (1978) re: inapproximability

In general, submodular maximization over a knapsack constraint is $(1 - 1/e)$-inapproximable (Kulik et al. 2013), so the existence of an FPTAS for Ellis's problem is a significant result.
\end{frame}
} \else {
\begin{frame}{해법 개관}
대학 지원 문제를 2개의 경우로 나눌 수 있다.
\begin{itemize}
\item \textbf{알마의 문제:} 모든 $g_j = 1$, 즉 배낭 제약 대신 집합 크기 제약이 있는 특수한 경우.

@@

\looseness=-1
일반적으로, 배낭 제약식 위에서 submodular 함수를 최대화하는 문제는 $(1 - 1/e)$보다 좋은 근사 계수를 가지는 해법이 존재하지 않으므로 (Kulik et al. 2013), 엘리스 문제에 FPTAS가 존재하는 것은 의미가 있는 결과다.
\end{frame}
} \fi

@@

In the paper, we show that setting $P \gets \bigl\lceil\log_{10}\left(m^2 / \varepsilon \bar U\right)\bigr\rceil$ guarantees a $(1- \varepsilon)$-optimal portfolio, and that this yields a table of size $O(m^3 / \varepsilon)$, meaning that this algorithm is \textbf{an FPTAS}.
\else
이제 $G[j, v]$-값을 표에 채우면 근사 최적 포트폴리오를 구할 수 \rlep{있다.}

@@

>>>>

In general, submodular maximization over a knapsack constraint is $(1 - 1/e)$-inapproximable (Nemhauser and Wolsey 1978; Kulik et al. 2013), so the existence of an FPTAS for Ellis's problem is a significant result.
\end{frame}
} \else {
\begin{frame}{해법 개관}
대학 지원 문제를 2개의 경우로 나눌 수 있다.
\begin{itemize}
\item \textbf{알마의 문제:} 모든 $g_j = 1$, 즉 배낭 제약 대신 집합 크기 제약이 있는 특수한 경우.

@@

\looseness=-1
일반적으로, 배낭 제약식 위에서 submodular 함수를 최대화하는 문제는 $(1 - 1/e)$보다 좋은 근사 계수를 가지는 해법이 존재하지 않으므로 (Nemhauser and Wolsey 1978; Kulik et al. 2013), 엘리스 문제에 FPTAS가 존재하는 것은 의미가 있는 결과다.
\end{frame}
} \fi

@@

In the paper, we show that setting $P \gets \bigl\lceil\log_{10}\left(m^2 / \varepsilon \bar U\right)\bigr\rceil$ guarantees a $(1- \varepsilon)$-optimal portfolio, and that this yields a table of size $O(m^3 / \varepsilon)$, meaning that this algorithm is \textbf{an FPTAS}.
\else
이제 $G[j, v]$-값을 표에 채우면 근사 최적 포트폴리오를 구할 수 \rlap{있다.}

@@

Nemhauser, George and Laurence Wolsey. 1978. ``Best Algorithms for Approximating the Maximum of a Submodular Set Function.'' \emph{Mathematics of Operations Research} 3 (3): 177--88. \url{https://doi.org/10.1287/moor.3.3.177}.
